---
title: "ETC5521 Assignment 1"
subtitle: "Global Fishing"
team: [EMU]
author:
  - [Min Min Soh]
  - [Rohan Baghel]

date: "`r Sys.Date()`"
output:
   bookdown::html_document2:
    toc: yes
    df_print: paged
    number_sections: yes
    fig_caption: yes

---

[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "images/",
                      fig.align = "center")
```

# Introduction and motivation

Global fishing receives a great deal of attention in the media for the past decades. The rise of world population has increased the demand for seafood across the world. Coastal countries mainly rely on fishing as one of the most important food sources. Our first research question would learn about seafood consumption of countries over time. We’ll also study about how much seafood are being produced by each country overtime.

Meanwhile, the health of fish population in the world remains as a concern with the rise of global fishing. It then prompts us to assess how much of fish stocks are caught within the sustainable levels over the years without over exploiting the fish populations.

Fish farming (or ‘aquaculture’)helps to contribute to the seafood production while alleviating the pressure of wild fisheries. This inspires us to further analyse the trend of aquaculture as compared to wild fish catch over time.

We begin by describing the data in the next section, how we source it and how we prepare the data for analysis. In the analysis section, we present our observations through graphical displays. Our main tool is R, a programming language for statistical computing and graphics.
 

# Data description 


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(tidytuesdayR)
library(plotly)
library(bookdown)
library(visdat)
library(patchwork)
library(maps)
library(kableExtra)
library(readr)
library(ggridges)
library(gganimate)
library(transformr)
library(gifski)
library(viridis)
library(png)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

captured_vs_farmed <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-12/capture-fisheries-vs-aquaculture.csv')

consumption <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-12/fish-and-seafood-consumption-per-capita.csv')

stock <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-12/fish-stocks-within-sustainable-levels.csv')

production <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-12/seafood-and-fish-production-thousand-tonnes.csv')

fishery <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-12/global-fishery-catch-by-sector.csv')
```


# Expected findings 

## What would be the notable finding when we comparing the consumption with production?






### Visualization and analysis

Figure \@ref(fig:worldconsumption) depicts the growing trend in world seafood consumption from 1969 and 2018. The average yearly seafood consumption for one person was 13.8kg, while it increased to 20kg in recent time. Moreover, it is obviously that between 1990 and 1992, the average seafood consumption decreased, mostly because of economic problems in low-income nations such those in Africa, Latin America, the Caribbean, and the Near East. This resulted in increased pressure on many items' prices (Dumas, 1992). Seafood consumption has grown globally as the crisis has subsided. Overall, this is consistent with our assumption that seafood consumption would continue to rise.

The line plot \@ref(fig:production)of world yearly seafood production shows an upward trend from 1969 to 2018. In 1970, the average production of seafood is 118 million metric tons. While the production became 3 times greater in recent year. And the production decreasing period happened same with the seafood consumption. We can make assumption that there has a positive relationship between seafood consumption and production. 


```{r}
new_con <- consumption %>% 
    filter(Year >= 1969) %>%  
     select(-Code)

con_cap <-new_con %>% 
  left_join(captured_vs_farmed, by = c("Entity","Year")) %>% 
  rename(`seafood consumption(kg/capita/yr)` = `Fish, Seafood- Food supply quantity (kg/capita/yr) (FAO, 2020)`) %>% 
  select(-Code) 

con_cap$`Total production(metric tons)` = rowSums(con_cap[, c("Aquaculture production (metric tons)","Capture fisheries production (metric tons)")])

```

```{r worldconsumption, echo=FALSE, warning = FALSE, message = FALSE, preserve = TRUE, fig.pos = 'H', out.extra = "", fig.cap = "Average seafood consumption in the world over time"}
avg_con <- con_cap %>% 
  group_by(Year) %>%  
  summarise(`average consumption` = mean(`seafood consumption(kg/capita/yr)`),
            `Total production` = sum(`Total production(metric tons)`, na.rm = TRUE), 
            `Total Aquaculture production`=sum(`Aquaculture production (metric tons)`, na.rm = TRUE), 
            `Total Capture fisheries production`=sum(`Capture fisheries production (metric tons)`, na.rm = TRUE) ) %>%  
filter (Year <= 2013)
  

avgcon <- avg_con %>% 
  ggplot(aes(x = Year, y = `average consumption`)) + 
  geom_line(colour = "red") +
  labs(y = "Average Seafood Consumption (kg) per person per year") 

ggplotly(avgcon)

```

```{r production, echo=FALSE, warning = FALSE, message = FALSE, preserve = TRUE, fig.pos = 'H', out.extra = "", fig.cap = "Average yearly seafood production in the world over time"}
totalpro <- avg_con %>%  ggplot(aes(x = Year, y = `Total production`/1000000)) + 
  geom_line(colour = "blue") +
  labs(y = "World Total Production of Seafood(metric tons)") 
  
ggplotly(totalpro)

```




```{r contribution, warning = FALSE, message = FALSE, preserve = TRUE, fig.pos = 'H', out.extra = "", fig.cap = "Contribution of top 10 seafood producer 2015-2018(metric tons)"}

captured_vs_farmed1  <- captured_vs_farmed %>% 
  rename(aquaculture = `Aquaculture production (metric tons)`,
         captured = `Capture fisheries production (metric tons)`)%>% 
  mutate(Entity = toupper(Entity))


captured_vs_farmed_long  <- captured_vs_farmed1 %>% pivot_longer(cols = aquaculture:captured,
                                                           names_to = "production_type",
                                                           values_to = "production")


world_cap_farm <- captured_vs_farmed_long %>% filter(Entity =="WORLD")


world_cap_farmlong <- world_cap_farm %>% pivot_wider(names_from = production_type, values_from= production )%>%
  mutate(total= aquaculture+ captured)%>%
  filter(Year== 2015)
  


dat <- iso3166 %>% 
  mutate(ISOname = toupper(ISOname))  %>%
  rename(Entity = ISOname)

country_cf <- inner_join(captured_vs_farmed1, dat, by = "Entity")

avg_contribution1 <- country_cf %>% 
  filter (Year >= 2015) %>%
  group_by(Entity)%>%
  summarise(avg_captured = mean(captured, na.RM = TRUE),
            avg_aquaculture = mean(aquaculture, na.RM = TRUE))%>%
  arrange(-avg_aquaculture) %>%
  mutate(total= avg_captured+avg_aquaculture)%>%
  arrange(-total) %>%
  mutate(rank = row_number())%>%
  filter(rank %in% 1:10) %>%
  mutate(across(avg_captured:avg_aquaculture, ~ scales::label_comma()(.x))) %>%
  rename(`Average_captured` = avg_captured,
         `Average_aquaculture` = avg_aquaculture)



avg_contribution2015 <-   avg_contribution1 %>%mutate(contribution= total/world_cap_farmlong$total)
   
   
Graph.5g <- ggplot(avg_contribution2015,aes(x=reorder(Entity, (contribution)), y=contribution, fill=Entity))+
  geom_col()+
   theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x = "Entity", y = "Average production (metric tons)")+
  coord_flip()


ggplotly(Graph.5g)
```
The bar plot \@ref(fig:contribution) shows the contributions of top 10 seafood producer by country. China is the largest contributor and provide 40% seafood of the whole world in recent years. Indonesia and India produce 11% and 5.6% respectively. It's intriguing to note that except US produce 3% and Norway produce 1% of the seafood other major producers are from Asia. 

```{r scatter, echo=FALSE, warning = FALSE, message = FALSE, preserve = TRUE, fig.pos = 'H', out.extra = "", fig.cap = "Relationship between seafood consumption and production"}
ggscatmat(avg_con, 
          columns = 2:ncol(avg_con)) 
```
To explore relationship between seafood consumption and seafood production, we made a scatter matrix plot \@ref(fig:scatter). Since seafood produce in two ways: aquaculture and capture, we add another two variables `Aquaculture production` and `Capture production`to do the scatter plot and try to find some interest between each variable. The outcome demonstrates a strong positive correlation between each variable. There is a significant linear positive relation between average consumption and total production as we expected.The correlation coefficient is 0.97 almost reach to 1. Moreover, the two methods used to produce fish also has a positive linear relation.

### Summary and findings 

1. 
2. 



## Compare production of 7 different fish type. Which type of seafood contribute the most to meet the increasing demand? 









# References

Becker OScbRA, Minka ARWRvbRBEbTP, Deckmyn. A (2021). _maps: Draw Geographical Maps_. R
  package version 3.4.0, <https://CRAN.R-project.org/package=maps>.

C. Sievert. Interactive Web-Based Data Visualization with R, plotly, and shiny. Chapman and
  Hall/CRC Florida, 2020.

Dumas, M. W. (1992). Productivity trends: prepared fish and seafoods industry. Monthly Lab. Rev., 115, 3.

Hughes E (2022). _tidytuesdayR: Access the Weekly 'TidyTuesday' Project Dataset_. R package version
  1.0.2, <https://CRAN.R-project.org/package=tidytuesdayR>.
  
H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016.


Ooms J (2022). _gifski: Highest Quality GIF Encoder_. R package version 1.6.6-1,
  <https://CRAN.R-project.org/package=gifski>.
  
Pedersen T, Robinson D (2020). _gganimate: A Grammar of Animated Graphics_. R package
  version 1.0.7, <https://CRAN.R-project.org/package=gganimate>.

Pedersen T (2020). _patchwork: The Composer of Plots_. R package version 1.1.1,
  <https://CRAN.R-project.org/package=patchwork>.

Pedersen T (2020). _transformr: Polygon and Path Transformations_. R package version 0.1.3,
  <https://CRAN.R-project.org/package=transformr>.
  
Salinas, E., Van Doorn, R., & Redaelli, S. (2015). Maldives: Identifying Opportunities and Constraints to Ending Poverty and Promoting Shared Prosperity.

Simon Garnier, Noam Ross, Robert Rudis, Antônio P. Camargo, Marco Sciaini, and Cédric
  Scherer (2021). Rvision - Colorblind-Friendly Color Maps for R. R package version 0.6.2.
  
  
Simon Garnier, Noam Ross, Robert Rudis, Antônio P. Camargo, Marco Sciaini, and Cédric Scherer (2021).   Rvision - Colorblind-Friendly Color Maps for R.

Subasinghe, R., Soto, D., & Jia, J. (2009). Global aquaculture and its role in sustainable   development. Reviews in aquaculture, 1(1), 2-9.

Tierney N (2017). “visdat: Visualising Whole Data Frames.” _JOSS_, *2*(16), 355.
  doi:10.21105/joss.00355 <https://doi.org/10.21105/joss.00355>,
  <http://dx.doi.org/10.21105/joss.00355>.

Urbanek S (2013). _png: Read and write PNG images_. R package version 0.1-7,
  <https://CRAN.R-project.org/package=png>.

Wang, P., Ji, J., & Zhang, Y. (2020). Aquaculture extension system in China: development, challenges, and prospects. Aquaculture reports, 17, 100339.

Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry
  L, Hester J, Kuhn M, Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel
  DP, Spinu V, Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019). “Welcome to the
  tidyverse.” _Journal of Open Source Software_, *4*(43), 1686. doi:10.21105/joss.01686
  <https://doi.org/10.21105/joss.01686>.

Wickham H, Hester J, Bryan J (2022). _readr: Read Rectangular Text Data_. R package version
  2.1.2, <https://CRAN.R-project.org/package=readr>.

Wilke C (2021). _ggridges: Ridgeline Plots in 'ggplot2'_. R package version 0.5.3,
  <https://CRAN.R-project.org/package=ggridges>.
  
Yihui Xie (2022). bookdown: Authoring Books and Technical Documents with R Markdown. R
  package version 0.26.

Zhu H (2021). _kableExtra: Construct Complex Table with 'kable' and Pipe Syntax_. R package
  version 1.3.4, <https://CRAN.R-project.org/package=kableExtra>.


```{r, echo = FALSE}
sessioninfo::session_info()
```
